### 2016-06-30 paper/evaluation.tex
added in full table figure

>>>>

\begin{figure*}
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline
\bfseries Test & \bfseries ForceExpandTime & \bfseries ForceExpandExamplesRequired
& \bfseries Computation Time & \bfseries Examples Required
\csvreader[head to column names]{generated-data/data.csv}{}
{\\\hline\Test & \ForceExpandTime & \ForceExpandExamplesRequired & \ComputationTime & \ExamplesRequired}
\\\hline
\end{tabular}

\end{figure*}
